---
title: "Data_Analysis_V2"
author: "Joan Moreaux and Meredith Miller"
date: "22/11/2021"
output: pdf_document
---

```{r, warning=FALSE, message=FALSE}
library(performance)
library(DHARMa)
library(mgcv)
library(fitdistrplus)
library(goft)
library(gamlss)
library(FSA) 
library(fGarch)
library(LambertW)
library(ordinal)
library(cowplot)
library(tidyverse)
```

```{r, warning=FALSE, message=FALSE}
health_data <- read.csv("Big_Data_Green.csv")
heat_data <- read.csv("Heat_Data.csv")
```

## Health Data
Includes feeding time, PAM measurements, base measurements, and symbiont density 

```{r, warning=FALSE, message=FALSE}
health_data <- health_data %>% 
  mutate(Fv_Fm_1 = as.numeric(Fv_Fm_1), PAM_avg = ((Fv_Fm_1 + Fv_Fm_2 + Fv_Fm_3)/3)) %>% 
  mutate(Base_Diameter_mm = (Base_Width + Base_Length + Base_Diagonal)/3) %>%
  mutate(Weight_Tentacle_mg = Weight_Tentacle_g*1000) %>% 
  mutate(Green_Density = (Green_Cells/1)*(1/0.1)*(1/0.001)*(0.5/Weight_Tentacle_mg)) %>% 
  mutate(Dino_Density = (Dino_Cells/1)*(1/0.1)*(1/0.001)*(0.5/Weight_Tentacle_mg)) %>%
  mutate(MI_Green = (Div_Green/Green_Cells)*100, MI_Dino = (Div_Dino/Dino_Cells)*100) %>% #Bates et al. 2010
  mutate(Bucket = as.factor(Bucket), Treatment = as.factor(Treatment), Date = as.factor(Date), Event = as.factor(Event), 
         Species_ID = as.factor(Species_ID), Field_Site = as.factor(Field_Site), Event_True = as.factor(Event_True)) %>% 
  filter(Species_ID != "G32B" & Species_ID != "G33B") %>% 
  mutate(Treatment = fct_relevel(Treatment, "Control", "25C", "30C"))
cols_for_heat = c("25C" = "brown2", "30C" = "darkred", "Control" = "azure4")
```

### PAM data
```{r}
PAM_data <- health_data %>% 
  select(-c(Field_Site, Acclimation_Period, Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, Nb_Tentacles, 
            Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, Green_Cells, Dino_Cells, 
            Feeding_Time_Min, Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, Removed, Div_Green, Div_Dino, MI_Green,
            MI_Dino, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3)) %>% 
  drop_na(PAM_avg) %>% 
  drop_na(Event_True) %>% 
  drop_na(Time_Point) %>% 
  filter(Species_ID != "G32B" & Species_ID != "G33B") %>%
  filter(Green_Density < 1000 | Dino_Density < 1000) %>% 
  group_by(Treatment, Date) %>% 
  mutate(PAM_per_Treatment = mean(PAM_avg))
```

```{r, warning=FALSE, message=FALSE}
shapiro.test(PAM_data$PAM_avg) # p-value < 0.05, distribution is not normal
bartlett.test(PAM_avg ~ Treatment, data = PAM_data) # p-value < 0.05, does not meet equal variance assumptions
```

Our data does not meet the assumption and therefore we will not be able to use tests such as ANOVA and linear models. 

Checking distribution:
If we get get a p-value < 0.5, then they is a significant differnce between the data and the distribution, and therefore this model should not be used in our analyse.

```{r, warning=FALSE, message=FALSE}
exp_test(PAM_data$PAM_avg)        #p-value < 2.2e-16, cannot use
gamma_test(PAM_data$PAM_avg)      #p-value < 0.00334, cannot use
lnorm_test(PAM_data$PAM_avg)      #p-value = 1.97e-07, cannot use
normal_test(PAM_data$PAM_avg)     #p-value = 0.002704, cannot use
weibull_test(PAM_data$PAM_avg)    #p-value < 0.05, cannot use
```

Since we cannot use any that we learned in class, we are using fitDist to check many distributions at once. fitDist showed that the SHASH distribution fits the best with our data, so we can use histDist to visualize it. 

**SHASH Distribution Graph for PAM Data**
```{r, warning=FALSE, message=FALSE}
#Look for anemone resiliancy Fv/Fm

PAM_visual <- fitDist(PAM_avg, data = PAM_data, type = "realAll", try.gamlss = T)
PAM_visual

#Visualizing fistDist

histDist(y, family = SHASH, density = FALSE, 
        nbins = 10, xlab = "x", ylab = "y", data = PAM_visual, 
        col.hist = "gray", border.hist = "blue", 
        fg.hist = rainbow(12)[9])
```

Initially we ran this data and it told us to use a SHASH distribution. [Family:  c("SHASH", "Sinh-Arcsinh"), Fitting method: "nlminb" with 12% error, Call:  gamlssML(formula = y, family = DIST[i])]. After running the data again with updates to our PAM threshold, it was suggested to use the BCEP distribution [Family:  c("BCPE", "Box-Cox Power Exponential"), Call:  gamlss(formula = y ~ 1, family = DIST[i], trace = FALSE)]. After visualizing both the SHASH and BCEP distributions with our updated data, we decided to stick with SHASH since the distribution seemed to fit better. 

```{r, warning=FALSE, message=FALSE}
# Modelling fitDist
PAM_model <- gamlss(formula = PAM_avg ~ Time_Point*Treatment + random(Species_ID), family = SHASH(), data = PAM_data, control = gamlss.control(n.cyc = 200))

summary(PAM_model)
```
Findings:
* Time point and 25C is signifigant, 30C is not
* Plot avg fv/fm over all time points (this was signifigantly different over time)