---
title: "Data Analysis"
author: "Joan Moreaux and Meredith Miller"
date: "22/11/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=TRUE, tidy.opts = list(width.cutoff = 80))
```

## Loading library and data

```{r, warning=FALSE, message=FALSE}
library(performance)
library(DHARMa)
library(mgcv)
library(fitdistrplus)
library(goft)
library(gamlss)
library(FSA) 
library(fGarch)
library(LambertW)
library(ordinal)
library(cowplot)
library(here)
library(plotrix)
library(patchwork)
library(tidyverse)
```

```{r, warning=FALSE, message=FALSE}
health_data <- read.csv(here("./data/Big_Data_Green.csv"))
heat_data <- read.csv(here("./data/Heat_Data.csv"))
```

## Health Data
Includes feeding time, PAM measurements, base measurements, and symbiont density.

```{r, warning=FALSE, message=FALSE}
# Organizing the data, adding average PAM, average base diameter, and symbiont density
health_data <- health_data %>% 
  mutate(Fv_Fm_1 = as.numeric(Fv_Fm_1), PAM_avg = ((Fv_Fm_1 + Fv_Fm_2 + Fv_Fm_3)/3)) %>% 
  mutate(Base_Diameter_mm = (Base_Width + Base_Length + Base_Diagonal)/3) %>%
  mutate(Weight_Tentacle_mg = Weight_Tentacle_g*1000) %>% 
  mutate(Green_Density = (Green_Cells/1)*(1/0.1)*(1/0.001)*(0.5/Weight_Tentacle_mg)) %>% 
  mutate(Dino_Density = (Dino_Cells/1)*(1/0.1)*(1/0.001)*(0.5/Weight_Tentacle_mg)) %>%
  mutate(MI_Green = (Div_Green/Green_Cells)*100, 
         MI_Dino = (Div_Dino/Dino_Cells)*100) %>% # Bates et al. 2010
  mutate(Bucket = as.factor(Bucket), Treatment = as.factor(Treatment), 
         Date = as.factor(Date), Event = as.factor(Event), 
         Species_ID = as.factor(Species_ID), Field_Site = as.factor(Field_Site), 
         Event_True = as.factor(Event_True)) %>% 
  filter(Species_ID != "G32B" & Species_ID != "G33B") %>% 
  mutate(Treatment = fct_relevel(Treatment, "Control", "25C", "30C"), 
         Event = fct_relevel("Acclimation", "Pre-heat", "Post-heat", "Recovery")) 
cols_for_heat = c("25C" = "sienna2", "30C" = "brown3", "Control" = "azure4")
```

### Symbiont Data
#### PAM Threshold
Determining a mimum threshold for aposymbiotic anemones that we will remove from the PAM data. From the data bellow, we decide that the threshold for PAM will be >1000 cells per mg (symbiont density).

```{r, warning=FALSE, message=FALSE}
Green_Threshold <- health_data %>% 
  select(-c(Event, Field_Site, Acclimation_Period, Base_Width, Base_Length, 
            Base_Diagonal, Base_Diameter_mm, Nb_Tentacles, Weight_Total_g, 
            Weight_Tube_g, Weight_Tentacle_g, Div_Dino, Dino_Cells, Feeding_Time_Min, 
            Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, Removed, MI_Dino, 
            Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, Event_True, Dino_Density)) %>% 
  drop_na(Green_Density) %>% 
  drop_na(Time_Point) %>% 
  filter(Green_Density != 0)

Dino_Threshold <- health_data %>% 
  select(-c(Event, Field_Site, Acclimation_Period, Base_Width, Base_Length, 
            Base_Diagonal, Base_Diameter_mm, Nb_Tentacles, Weight_Total_g, 
            Weight_Tube_g, Weight_Tentacle_g, Green_Cells, Div_Green, Feeding_Time_Min, 
            Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, Removed, MI_Green, 
            Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, 
            PAM_avg, Event_True, Green_Density)) %>% 
  drop_na(Dino_Density) %>% 
  drop_na(Time_Point) %>% 
  filter(Dino_Density != 0)
```

#### Density Data
Data for models of symbiont density for both zoochlorellae and zooxanthellae. It filters out unwanted columns and anemones without symbiont count.

```{r, warning=FALSE, message=FALSE}
# Organizing the data 
Green_Symbionts <- health_data %>% 
  select(-c(Event, Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, 
            Nb_Tentacles, Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, 
            Green_Cells, Dino_Cells, Feeding_Time_Min, Feeding_Time, Feeding_Start,
            Feeding_Stop, Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, 
            Event_True)) %>% 
  filter(Date == "11/5/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021", "11/13/2021")) %>% 
  mutate(Green_Density_Log = log(Green_Density)) %>% 
  drop_na(Green_Density) %>% 
  drop_na(Dino_Density) %>% 
  drop_na(MI_Green) %>% 
  drop_na(MI_Dino) %>% 
  filter(Green_Density != 0) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period)) %>% 
  group_by(Treatment, Date) %>% 
  mutate(Mean_Green_Log = mean(Green_Density_Log), 
         SE_Green_Log = std.error(Green_Density_Log)) 

Dino_Symbionts <- health_data %>% 
  select(-c(Event, Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, 
            Nb_Tentacles, Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, 
            Green_Cells, Dino_Cells, Feeding_Time_Min, Feeding_Time, 
            Feeding_Start, Feeding_Stop, Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, 
            Fv_Fm_3, PAM_avg, Event_True)) %>% 
  filter(Date == "11/5/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021", "11/13/2021")) %>% 
  drop_na(Green_Density) %>% 
  drop_na(Dino_Density) %>% 
  drop_na(MI_Green) %>% 
  drop_na(MI_Dino) %>% 
  filter(Dino_Density != 0) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period))
```

**Checking Normality and Equal Variance:**

```{r, warning=FALSE, message=FALSE}
# Green
shapiro.test(Green_Symbionts$Green_Density)      
bartlett.test(Green_Density ~ Treatment, Green_Symbionts)      

# Dino
shapiro.test(Dino_Symbionts$Dino_Density) 
bartlett.test(Dino_Density ~ Treatment, Dino_Symbionts)
```

All p-values are <0.05 and therefore the distributions do not meet assumptions of normality and equal variance. 

**Checking Distributions of Symbiont Data:** Determining if the data fits other distributions. 

```{r, out.width = "70%", out.height = "57%", warning=FALSE, message=FALSE}
#Greens
exp_test(Green_Symbionts$Green_Density)         #p-value < 0.05
gamma_test(Green_Symbionts$Green_Density)       #p = 0.123
lnorm_test(Green_Symbionts$Green_Density)       #p-value < 0.05
normal_test(Green_Symbionts$Green_Density)      #p-value < 0.05
weibull_test(Green_Symbionts$Green_Density)     #p = 0.44

#Use Weibull since p value is larger than gamma
Green_Weibull <- histDist(Green_Symbionts$Green_Density, "WEI", 
                          density = F, main = "Weibull")

#Dinos
exp_test(Dino_Symbionts$Dino_Density)           #p-value > 0.05
gamma_test(Dino_Symbionts$Dino_Density)         #p = 0.6709
lnorm_test(Dino_Symbionts$Dino_Density)         #p-value < 0.05
normal_test(Dino_Symbionts$Dino_Density)        #p-value < 0.05
weibull_test(Dino_Symbionts$Dino_Density)       #p = 0.774

#Use Gamma since p value is larger than weibull
Dino_Gamma <- histDist(Dino_Symbionts$Dino_Density, "GA", 
                       density = F, main = "Gamma")
```

**Running Models on Symbiont Data:**
We chose to use our Weibull distribution for green density and Gamma distribution for dino density. Here we run our models.

```{r, warning=FALSE, message=FALSE}
#Green
Green_Symbionts$orderTreatment = ordered(Green_Symbionts$Treatment, 
                                         levels = c("Control", "25C", "30C"))

Green_Weibull_model <- gamlss(formula = Green_Density ~ Date*Treatment +
                                random(Species_ID) + random(Field_Site) + 
                                random(Acclimation_Period), 
                              family = WEI(), data = Green_Symbionts, 
                              control = gamlss.control(n.cyc = 10))

summary(Green_Weibull_model) # significance in the 30 degree treatment

#Dino
Dino_Symbionts$orderTreatment = ordered(Dino_Symbionts$Treatment, 
                                        levels = c("Control", "25C", "30C"))

Dino_Gamma_model <- gamlss(formula = Dino_Density ~ Date*Treatment + 
                             random(Species_ID) + random(Field_Site) + 
                             random(Acclimation_Period), 
                           family = GA(), data = Dino_Symbionts, 
                           control = gamlss.control(n.cyc = 3))

summary(Dino_Gamma_model) # significance in both the 25 and 30 degree treatment
```

**Table 1**: ZC symbiont density, using gamlss with Weibull distribution. Significance compared to pre-heat of control.

| Model Terms | Estimate | Standard Error | t-value | p-value |
| ----------------- | -------- | -------- | -------- | -------- |
| [Intercept] | 7.02648  |  0.20520 | 34.242 | < 0.01 |
| Post-heat | -0.17523  |  0.27804 | -0.630 | 0.5354 | 
| Recovery | 0.28886  |  0.28856  | 1.001 |  0.3283 |   
| Mid heatwave | -0.12147  |  0.32291 | -0.376 | 0.7106 |  
| Extreme heatwave | 1.47524  |  0.26344  | 5.600 | < 0.01 |
| Post-heat : Mid heatwave | 0.05102  |  0.45057  | 0.113 |  0.9109 |   
| Post-heat : Extreme heatwave |-0.83396  |  0.44295 | -1.883 |  0.0738 |  
| Recovery : Mid heatwave | 0.13530  |  0.38302 |  0.353 |  0.7275 | 
| Recovery : Extreme heatwave  | 0.32660  |  0.38314  | 0.852  | 0.4037 | 

**Table 2**: ZX symbiont density, using gamlss with Gamma distribution. Significance compared to pre-heat of control.

| Model Terms | Estimate | Standard Error | t-value | p-value |
| ----------------- | -------- | -------- | -------- | -------- |
| [Intercept] | 8.06079  |  0.25027 | 32.208 | < 0.01 |
| Post-heat | -0.16934  |  0.34106 | -0.496 | 0.6245 |    
| Recovery | -0.23477  |  0.35394 | -0.663 | 0.5141 |   
| Mid heatwave | -1.32556  |  0.39574 | -3.350 | 0.0029 |
| Extreme heatwave | -0.74465  |  0.32308 | -2.305 | 0.0310 |
| Post-heat : Mid heatwave | 0.43494  |  0.55161  | 0.788 |  0.4389 |   
| Post-heat : Extreme heatwave | 1.03874  |  0.54261 | 1.914 | 0.0687 |  
| Recovery : Mid heatwave | -0.23333 | 0.46976 | -0.497 | 0.6244 |    
| Recovery : Extreme heatwave | 0.03936 | 0.46977 | 0.084 | 0.9340 |    

**Dunn and Kruskal Wallis Test on Density Data:**
Used for box blot

```{r}
kruskal.test(Green_Density ~ Treatment, data = Green_Symbionts) # p = 0.004
dunnTest(Green_Density ~ Treatment, data = Green_Symbionts) 
# sig. difference between 25-30 and between 30-control

kruskal.test(Dino_Density ~ Treatment, data = Dino_Symbionts) # not significant 
dunnTest(Dino_Density ~ Treatment, data = Dino_Symbionts) # not significant 
```

**Plots for symbiont data:**
Box plot with event on the x axis and logged symbiont density on the y axis, separated by treatment.

```{r, warning=FALSE, message=FALSE}

treatment_labels = c("Control", "Mid heatwave", "Extreme heatwave")
names(treatment_labels) = (c("Control", "25C", "30C"))
green_plot <- ggplot(Green_Symbionts, aes(x = Date, y = log(Green_Density), 
                                          fill = Treatment)) +
  geom_boxplot(alpha = 0.85) +
  xlab("Event") +
  ylab("Log-transformed ZC density (cells/mg)") +
  facet_grid(. ~ Treatment, 
             labeller = labeller(Treatment = treatment_labels)) +
  scale_fill_manual(limits = c("Control", "25C", "30C"),
                    labels = c("Control", "Mid heatwave", "Extreme heatwave"),
                    values = cols_for_heat) +
  theme_test()

green_plot <- green_plot + ylim(0,12) + 
  scale_x_discrete(labels=c("11/5/2021" = "Pre-heat", "11/9/2021" = "Post-heat",
                            "11/13/2021" = "Recovery")) 

dino_plot <- ggplot(Dino_Symbionts, aes(x = Date, y = log(Dino_Density), 
                                        fill = Treatment)) +
  geom_boxplot(alpha = 0.85) +
  xlab("Event") +
  ylab("Log-transformed S density (cells/mg)") +
  facet_grid(. ~ Treatment,
             labeller = labeller(Treatment = treatment_labels)) +
  scale_fill_manual(limits = c("Control", "25C", "30C"),
                    labels = c("Control", "Mid heatwave", "Extreme heatwave"),
                    values = cols_for_heat) +
  theme_test()
dino_plot <- dino_plot + ylim(0,12) + 
  scale_x_discrete(labels=c("11/5/2021" = "Pre-heat", "11/9/2021" = "Post-heat",
                            "11/13/2021" = "Recovery"))

density_plot = (green_plot + dino_plot) + plot_layout(ncol=1)
density_plot <- density_plot + plot_annotation(tag_levels = 'A')
density_plot

ggsave(here("./images/density_plot.png"), density_plot, width = 10, height = 9)
```

#### Mitotic Index Data
MI is the amount of cell division in the symbionts, calculated as a %. 

```{r, warning=FALSE, message=FALSE}
# Organizing the data 
MI_Data <- health_data %>% 
  select(-c(Event, Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, 
            Nb_Tentacles, Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, 
            Green_Cells, Dino_Cells, Feeding_Time_Min, Feeding_Time, Feeding_Start, 
            Feeding_Stop, Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, 
            Event_True)) %>% 
  filter(Date == "11/5/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021", "11/13/2021")) %>% 
  drop_na(Green_Density) %>% 
  drop_na(Dino_Density) %>% 
  drop_na(MI_Green) %>% 
  drop_na(MI_Dino) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period)) %>% 
  mutate(MI_Dino_scaled = MI_Dino + 0.01) %>% 
  mutate(MI_Green_scaled = MI_Green + 0.01)
```

**Checking Normality and Equal Variance:**

```{r, warning=FALSE, message=FALSE}
#Green
shapiro.test(MI_Data$Green_Density)      
bartlett.test(Green_Density ~ Treatment, MI_Data)     

#Dino
shapiro.test(MI_Data$Dino_Density)     
bartlett.test(Dino_Density ~ Treatment, MI_Data) # p-value = 0.1483
```

ZC (green) symbiont density does not meet assumptions of normality or equal variance, while ZC (dino) does not meet assumption of normality but meets the assumption of equal variance. We will run Dunn and Kruskal Wallis tests on the MI data to test for significant differences.

**Dunn and Kruskal Wallis Test on MI Data:**

```{r}
kruskal.test(MI_Green ~ Treatment, data = MI_Data) # p = 0.009
dunnTest(MI_Green ~ Treatment, data = MI_Data) # sig. difference between 25-30

kruskal.test(MI_Dino ~ Treatment, data = MI_Data) # not significant 
dunnTest(MI_Dino ~ Treatment, data = MI_Data) # not significant 
```

**Plot for MI data:**
Box plot with event on the x axis and mitotic index on the y axis, separated by treatment.

```{r, warning=FALSE, message=FALSE}
green_MI_plot <- ggplot(Green_Symbionts, aes(x = Date, y = MI_Green, 
                                             fill = Treatment)) +
  geom_boxplot(alpha = 0.85) +
  xlab("Event") +
  ylab("ZC Mitotic Index (%)") +
  facet_grid(. ~ Treatment,
             labeller = labeller(Treatment = treatment_labels)) +
  scale_fill_manual(limits = c("Control", "25C", "30C"),
                    labels = c("Control", "Mid heatwave", "Extreme heatwave"),
                    values = cols_for_heat) +
  theme_test()
green_MI_plot <- green_MI_plot + ylim(0,60) + 
  scale_x_discrete(labels=c("11/5/2021" = "Pre-heat", "11/9/2021" = "Post-heat",
                            "11/13/2021" = "Recovery"))

dino_MI_plot <- ggplot(Dino_Symbionts, aes(x = Date, y = MI_Dino, 
                                           fill = Treatment)) +
  geom_boxplot(alpha = 0.85) +
  xlab("Event") +
  ylab("S Mitotic Index (%)") +
  facet_grid(. ~ Treatment,
             labeller = labeller(Treatment = treatment_labels)) +
  scale_fill_manual(limits = c("Control", "25C", "30C"),
                    labels = c("Control", "Mid heatwave", "Extreme heatwave"),
                    values = cols_for_heat) +
  theme_test()
dino_MI_plot <- dino_MI_plot + ylim(0,30) + 
  scale_x_discrete(labels=c("11/5/2021" = "Pre-heat", "11/9/2021" = "Post-heat",
                            "11/13/2021" = "Recovery"))

MI_plot = (green_MI_plot + dino_MI_plot) + plot_layout(ncol=1, heights=c(1.5,1))
MI_plot <- MI_plot + plot_annotation(tag_levels = 'A')
MI_plot

ggsave(here("./images/MI_plot.png"), MI_plot, width = 10, height = 9)
```

### PAM data
We filter out aposymbiotic anemones. 

```{r, warning=FALSE, message=FALSE}
# Organizing the data adding average and standard error Fv/Fm 
PAM_individuals <- health_data %>% 
  filter(Green_Density > 1000 | Dino_Density > 1000) %>% 
  distinct(Species_ID)

PAM_data <- health_data %>% 
  select(-c(Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, Nb_Tentacles,
            Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, Green_Cells, Dino_Cells, 
            Feeding_Time_Min, Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, 
            Removed, Div_Green, Div_Dino, MI_Green, MI_Dino, Acclimation_Period, 
            Green_Density, Dino_Density)) %>%
  drop_na(Time_Point) %>%
  drop_na(PAM_avg) %>%
  group_by(Treatment, Date) %>% 
  mutate(Mean_PAM = mean(PAM_avg), SE_PAM = std.error(PAM_avg))

filtered_PAM_data = PAM_individuals %>%
  left_join(PAM_data) %>% 
  filter(Date == "11/6/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  filter(Time_Point != 4) %>% 
  mutate(Date = fct_relevel(Date, "11/6/2021", "11/9/2021", "11/13/2021")) 
```

**Checking Normality and Equal Variance:**

```{r, warning=FALSE, message=FALSE}
shapiro.test(filtered_PAM_data$PAM_avg) 
bartlett.test(PAM_avg ~ Treatment, data = filtered_PAM_data) 
```

Our data does not meet the assumptions of normality and equal variance (p < 0.05) and therefore we will use Dunn and Kruskal Wallis tests to test for significant differences. 

```{r, warning=FALSE, message=FALSE}
kruskal.test(PAM_avg ~ Treatment, data = filtered_PAM_data) # significance
dunnTest(PAM_avg ~ Treatment, data = filtered_PAM_data) 
# significance only between 25 and 30
```

**Plot for PAM:**
Line plot with event on the x axis and average (+/- standard error) PAM measurements on the y axis, colour indicate treatments.

```{r, warning=FALSE, message=FALSE}
PAM_over_time <- ggplot(data = filtered_PAM_data, aes(x=Date, y = Mean_PAM, 
                                                      colour = Treatment, 
                                                      group = Treatment)) +
  geom_point(position = position_dodge(width = 0.1)) +
  geom_linerange(aes(ymin = Mean_PAM - SE_PAM, 
                     ymax = Mean_PAM + SE_PAM), position = position_dodge(width = 0.1)) +
  geom_line(position = position_dodge(width = 0.1)) +
  labs(x="Event",
       y = "Average Photosynthetic Efficiency (Fv/Fm)") +
  scale_colour_manual(limits = c("Control", "25C", "30C"),
                    labels = c("Control", "Mid heatwave", "Extreme heatwave"),
                    values = cols_for_heat) +
  theme_test()
PAM_over_time <- PAM_over_time + 
  scale_x_discrete(labels=c("11/6/2021" = "Pre-heat", "11/9/2021" = "Post-heat", 
                            "11/13/2021" = "Recovery"))
PAM_over_time

ggsave(here("./images/PAM_over_time.png"), PAM_over_time)
```

### Size Data
Measuring the size of the base as a proxy for weight. 

```{r, warning=FALSE, message=FALSE}
# Organizing the data and adding average and standard error of base size 
Size_Data <- health_data %>% 
  select(-c(Base_Width, Base_Length, Base_Diagonal, Nb_Tentacles, Weight_Total_g, 
            Weight_Tube_g, Weight_Tentacle_g, Weight_Tentacle_mg, Green_Cells, 
            Dino_Cells, Feeding_Time_Min, Feeding_Time, Feeding_Start, Feeding_Stop, 
            Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, Green_Density, 
            Dino_Density, MI_Green, MI_Dino, Div_Green, Div_Dino)) %>%
  filter(Date == "11/5/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021", "11/13/2021"), 
        (Treatment = fct_relevel(Treatment, "Control", "25C", "30C"))) %>% 
  drop_na(Base_Diameter_mm) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period)) %>% 
  group_by(Treatment, Date) %>% 
  mutate(Mean_Size = mean(Base_Diameter_mm), SE_Size = std.error(Base_Diameter_mm))
```

**Checking for Normality and Equal Variance:**

```{r, warning=FALSE, message=FALSE}
shapiro.test(Size_Data$Base_Diameter_mm)
bartlett.test(Base_Diameter_mm ~ Treatment, data = Size_Data)
```

The distributions do not meet assumptions of normality but does meet the assumption of equal variance. 

**Checking Distributions of Symbiont Data:**
Determining if the data fits other distributions. 

```{r, out.width = "70%", out.height = "57%", warning=FALSE, message=FALSE}
exp_test(Size_Data$Base_Diameter_mm)            #p-value < 0.05
gamma_test(Size_Data$Base_Diameter_mm)          #p = 0.1874
lnorm_test(Size_Data$Base_Diameter_mm)          #p = 0.4117
normal_test(Size_Data$Base_Diameter_mm)         #p-value < 0.05
weibull_test(Size_Data$Base_Diameter_mm)        #p-value < 0.05

# Run lnorm since it has the higest p value
Size_lnorm <- histDist(Size_Data$Base_Diameter_mm, "LOGNO", density = T, main = "lNorm")

# Choosing the best distribution by comparing AIC values
Size_lnorm <- histDist(Size_Data$Base_Diameter_mm, "LOGNO", density = T, main = "lNorm")
#AIC = 880.625
Feeding_Gamma <- histDist(Size_Data$Base_Diameter_mm, "GA", density = F, main = "Gamma")
#AIC = 883.161
```

**Running Models:**
We are going to run a lNorm model on our size data because the p value is larger and AIC value is smaller. 

```{r, warning=FALSE, message=FALSE}
Size_Data$orderTreatment = ordered(Size_Data$Treatment, levels = c("Control", "25C", "30C"))

Size_lNorm_model <- gamlss(formula = Base_Diameter_mm ~ Date*Treatment + 
                             random(Species_ID) + random(Field_Site) + 
                             random(Acclimation_Period), 
                           family = LOGNO(), data = Size_Data, 
                           control = gamlss.control(n.cyc = 4))
 summary(Size_lNorm_model) # significant in 30
```

The control and 25 did have significant values, but the 30 did not. 

**Table 3**: Size data, using gamlss with Log Normal distribution. Significance compared to pre-heat of control.

| Model Terms | Estimate | Standard Error | t-value | p-value |
| ----------------- | -------- | -------- | -------- | -------- |
| [Intercept] | 3.89112 | 0.01940 | 200.618 | < 0.01 |
| Post-heat | 0.03437 |  0.02685  | 1.280 | 0.2053 |   
| Recovery | 0.09388 |  0.02685  | 3.496 | < 0.01 |
| Mid heatwave | 0.03913  | 0.02685  | 1.457 | 0.1501 |    
| Extreme heatwave | 0.10920  | 0.02685  | 4.067 | < 0.01 |
| Post-heat : Mid heatwave |  0.03822 |  0.03756 |  1.018 | 0.3129 |    
| Post-heat : Extreme heatwave | -0.09243  | 0.03756 |  -2.461 | 0.0167 |  
| Recovery : Mid heatwave | -0.00411 | 0.03756 | -0.109 | 0.9133 |   
| Recovery : Extreme heatwave | -0.05528 | 0.03756 | -1.472 | 0.1462 | 

**Plot for Size:**
Line plot with event on the x axis and average (+/- standard error) base size measurements on the y axis, colour indicate treatments.

```{r, warning=FALSE, message=FALSE}
size_plot <- ggplot(data = Size_Data, aes(x=Date, y = Mean_Size, 
                                          colour = Treatment, group = Treatment)) +
  geom_point(position = position_dodge(width = 0.1)) +
  geom_linerange(aes(ymin = Mean_Size - SE_Size, ymax = Mean_Size + SE_Size), 
                 position = position_dodge(width = 0.1)) +
  geom_line(position = position_dodge(width = 0.1)) +
  labs(x="Event", 
       y = "Average Base Diameter (mm)") +
  scale_colour_manual(limits = c("Control", "25C", "30C"),
                    labels = c("Control", "Mid heatwave", "Extreme heatwave"),
                    values = cols_for_heat) +
  theme_test()

size_plot <- size_plot + 
  scale_x_discrete(labels=c("11/5/2021" = "Pre-heat", "11/9/2021" = "Post-heat", 
                            "11/13/2021" = "Recovery"))
size_plot

ggsave(here("./images/size_plot.png"), size_plot)
```

### Feeding Data
This is the feeding time before and after heatwaves. 

```{r, warning=FALSE, message=FALSE}
# Organizing the data 
Feeding_Data <- health_data %>% 
  select(-c(Base_Width, Base_Length, Base_Diagonal, Nb_Tentacles, Weight_Total_g, 
            Weight_Tube_g, Weight_Tentacle_g, Weight_Tentacle_mg, Green_Cells, 
            Dino_Cells, Base_Diameter_mm, Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, 
            Fv_Fm_3, PAM_avg, Green_Density, Dino_Density, MI_Green, MI_Dino,
            Div_Green, Div_Dino)) %>%
  filter(Date == "11/5/2021" | Date == "11/9/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021")) %>% 
  drop_na(Feeding_Time_Min) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period))
```

**Checking for Normality and Equal Variance:**

```{r, warning=FALSE, message=FALSE}
shapiro.test(Feeding_Data$Feeding_Time_Min)   
bartlett.test(Feeding_Time_Min ~ Treatment, data = Feeding_Data)
```

Distribution is not normal but meets the assumption of equal variance. We will check if it fits other distributions.  

**Checking Distributions:**
Determining if the data fits other distributions. 

```{r, out.width = "70%", out.height = "57%", warning=FALSE, message=FALSE}
exp_test(Feeding_Data$Feeding_Time_Min)            #p-value < 0.05
gamma_test(Feeding_Data$Feeding_Time_Min)          #p = 0.3717
lnorm_test(Feeding_Data$Feeding_Time_Min)          #p = 0.6937
normal_test(Feeding_Data$Feeding_Time_Min)         #p-value < 0.05
weibull_test(Feeding_Data$Feeding_Time_Min)        #p = 0.088

# Choosing the best distribution by comparing AIC value
Feeding_lnorm <- histDist(Feeding_Data$Feeding_Time_Min, "LOGNO", 
                          density = T, main = "lNorm") #AIC = 112.738
Feeding_Gamma <- histDist(Feeding_Data$Feeding_Time_Min, "GA", 
                          density = F, main = "Gamma") #AIC = 116.789
Green_Weibull <- histDist(Feeding_Data$Feeding_Time_Min, "WEI", 
                          density = F, main = "Weibull") #AIC = 115.143
```

**Running model:**
We are going to use the lnorm distribution because the p value is larger and AIC value is smaller.

```{r, warning=FALSE, message=FALSE}
Feeding_Data$orderTreatment = ordered(Feeding_Data$Treatment, 
                                      levels = c("Control", "25C", "30C"))

Feeding_lNorm_model <- gamlss(formula = Feeding_Time_Min ~ Date*Treatment + 
                                random(Species_ID) + random(Field_Site) + 
                                random(Acclimation_Period), 
                              family = LOGNO(), data = Feeding_Data, 
                              control = gamlss.control(n.cyc = 3))
summary(Feeding_lNorm_model) # significance is only in post-heat 30C
```

**Table 4**: Feeding data, using gamlss with Log Normal distribution. Significance compared to pre-heat of control.

| Model Terms | Estimate | Standard Error | t-value | p-value |
| ----------------- | -------- | -------- | -------- | -------- |
| [Intercept] | -0.5298 | 0.5149 | -1.029  | 0.3330 |
| Post-heat | 0.2449 | 0.7281 | -0.336 |  0.7451 |
| Mid heatwave | 0.8233 | 0.8141 |  1.011 |  0.3409 |
| Extreme heatwave | 0.3369 | 0.7281  | 0.463 |  0.6557  |
| Post-heat : Mid heatwave | 1.9684  |   1.1513 | 1.710 | 0.1249 |
| Post-heat : Extreme heatwave  | 2.3532  | 0.9970  | 2.360  | 0.0453 |

**Plot for Feeding:**
Box plot with event on the x axis and feeding time on the y axix, colours represent different treatments.

```{r, warning=FALSE, message=FALSE}
feeding_plot <- ggplot(Feeding_Data, aes(x = Date, y = Feeding_Time_Min, fill = Treatment)) +
  geom_boxplot(alpha=0.85) +
  xlab("Event") +
  ylab("Feeding Time (minutes)") +
  scale_fill_manual(limits = c("Control", "25C", "30C"),
                    labels = c("Control", "Mid heatwave", "Extreme heatwave"),
                    values = cols_for_heat) +
  theme_test()
feeding_plot <- feeding_plot + 
  scale_x_discrete(labels=c("11/5/2021" = "Pre-heat", "11/9/2021" = "Post-heat"))
feeding_plot
ggsave(here("./images/feeding_plot.png"), feeding_plot)
```

## Heat Data
Includes temperature during heatwave and behavioral responses (open vs closed)

```{r, warning=FALSE, message=FALSE}
# Data reorganization, adding average temp at each hour 
heat_data <- heat_data %>% 
  mutate(Open_Closed = as.factor(Open_Closed), Bucket = as.factor(Bucket), 
         Treatment = as.factor(Treatment), Field_Site = as.factor(Field_Site)) %>% 
  mutate(Open_Closed = fct_relevel(Open_Closed, "Open", "Partial", "Closed")) %>% 
  mutate(Treatment = fct_relevel(Treatment, "Control", "25C", "30C")) %>% 
  group_by(Treatment, Time_Block) %>% 
  mutate(Temp_avg = mean(Bucket_Temp))
```

**Temperature over Time Graph:**
Line plot with time in hours on the x axis and temperature on the y axis, colours represent different treatments. 

```{r, warning=FALSE, message=FALSE}
heat_plot <- ggplot(data = heat_data, aes(x = Time_Block, y = Temp_avg, color = Treatment)) +
  geom_point(size = 1) +
  geom_line(alpha = 1.5) +
  xlab("Time (hours)") +
  ylab("Temperature (°C)") +
  scale_colour_manual(limits = c("Control", "25C", "30C"),
                    labels = c("Control", "Mid heatwave", "Extreme heatwave"),
                    values = cols_for_heat) +
  theme(axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=10)) +
  theme_test() 
heat_plot <- heat_plot + theme(legend.key.size = unit(0.75, 'lines'))
heat_plot

ggsave(here("./images/heat_plot.png"), heat_plot)
```

### Ordinal Regression
Model to test significance on the open/partial/closed data. 

```{r}
ord_model = clmm(Open_Closed ~ Treatment + (1 | Bucket) + (1 | Species_ID), 
                 data = heat_data)
summary(ord_model) # significance in both treatments 
```

**Open/Closed Graph:**
Stacked bar plot with time in hours during heatwave on the x axis and frequency count on the y axis> The 3 bar plots are separated by treatment and the colours indicate different behaviours. 

```{r, warning=FALSE, message=FALSE}
behaviour_data <- heat_data %>% 
  group_by(Day, Treatment, Time_Block) %>% 
  count(Open_Closed)

behaviour_plot <- ggplot(data = behaviour_data, aes(x = Time_Block, y = n, fill = Open_Closed)) + 
  geom_bar(alpha = 0.95, position="fill", stat="identity") +
  facet_grid(. ~ Treatment,
             labeller = labeller(Treatment = treatment_labels)) +
  xlab("Time (hours)") +
  ylab("Frequency") +
  scale_fill_brewer(palette = "Greens") +
  theme_cowplot(10)
behaviour_plot <- behaviour_plot + labs(fill = "Behaviour Response")
behaviour_plot

ggsave(here("./images/behaviour_plot.png"), behaviour_plot, width = 10, height = 6)
```

