---
title: "Initial Data Analysis"
author: "Joan Moreaux and Meredith Miller"
date: "07/11/2021"
output:
  pdf_document: default
  html_document: default
---

```{r, warning=FALSE, message=FALSE}
library(performance)
library(DHARMa)
library(mgcv)
library(fitdistrplus)
library(goft)
library(gamlss)
library(FSA) 
library(fGarch)
library(LambertW)
library(ordinal)
library(cowplot)
library(here)
library(plotrix)
library(tidyverse)
```

```{r, warning=FALSE, message=FALSE}
health_data <- read.csv("Big_Data_Green.csv")
heat_data <- read.csv("Heat_Data.csv")
```

## Health Data
Includes feeding time, PAM measurements, base measurements, and symbiont density 

```{r, warning=FALSE, message=FALSE}
health_data <- health_data %>% 
  mutate(Fv_Fm_1 = as.numeric(Fv_Fm_1), PAM_avg = ((Fv_Fm_1 + Fv_Fm_2 + Fv_Fm_3)/3)) %>% 
  mutate(Base_Diameter_mm = (Base_Width + Base_Length + Base_Diagonal)/3) %>%
  mutate(Weight_Tentacle_mg = Weight_Tentacle_g*1000) %>% 
  mutate(Green_Density = (Green_Cells/1)*(1/0.1)*(1/0.001)*(0.5/Weight_Tentacle_mg)) %>% 
  mutate(Dino_Density = (Dino_Cells/1)*(1/0.1)*(1/0.001)*(0.5/Weight_Tentacle_mg)) %>%
  mutate(MI_Green = (Div_Green/Green_Cells)*100, MI_Dino = (Div_Dino/Dino_Cells)*100) %>% #Bates et al. 2010
  mutate(Bucket = as.factor(Bucket), Treatment = as.factor(Treatment), Date = as.factor(Date), 
         Event = as.factor(Event), Species_ID = as.factor(Species_ID), Field_Site = as.factor(Field_Site), 
         Event_True = as.factor(Event_True)) %>% 
  filter(Species_ID != "G32B" & Species_ID != "G33B") %>% 
  mutate(Treatment = fct_relevel(Treatment, "Control", "25C", "30C"), 
         Event = fct_relevel("Acclimation", "Pre-heat", "Post-heat", "Recovery"))
cols_for_heat = c("25C" = "brown2", "30C" = "darkred", "Control" = "azure4")
```

```{r}
nov_05 <- health_data %>% 
  filter(Date == "11/5/2021")

nov_09 <- health_data %>% 
  filter(Date == "11/9/2021")

delta_data = nov_05 %>%
  left_join(nov_09, by = "Species_ID") %>%
  mutate(Delta_Green_Density = Green_Density.y - Green_Density.x,
         Delta_Dino_Density = Dino_Density.y - Dino_Density.x,
         Field_Site = Field_Site.x,
         Acclimation_Period = Acclimation_Period.x,
         Treatment = Treatment.x) %>% 
  drop_na(Delta_Dino_Density, Delta_Green_Density) %>%
  select(Species_ID, Field_Site, Acclimation_Period, Treatment, Delta_Green_Density, Delta_Dino_Density)
```

### Symbiont Data
```{r, warning=FALSE, message=FALSE}
Green_Threshold <- health_data %>% 
  select(-c(Event, Field_Site, Acclimation_Period, Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, Nb_Tentacles, Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, Div_Dino, Dino_Cells, Feeding_Time_Min, Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, Removed, MI_Dino, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, Event_True, Dino_Density)) %>% 
  drop_na(Green_Density) %>% 
  drop_na(Time_Point) %>% 
  filter(Green_Density != 0)

Dino_Threshold <- health_data %>% 
  select(-c(Event, Field_Site, Acclimation_Period, Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, Nb_Tentacles, Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, Green_Cells, Div_Green, Feeding_Time_Min, Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, Removed, MI_Green, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, Event_True, Green_Density)) %>% 
  drop_na(Dino_Density) %>% 
  drop_na(Time_Point) %>% 
  filter(Dino_Density != 0)
```
From the data above, we decide that the threshold for PAM will be 1000 cells per mg (symbiont density).

### Density Data
The two datasets below are used in models for algae density and mitotic index of zoochlorellae and zooxanthellae. It filters out unwanted columns and drops NAs for Green_Density, Dino_Density, MI_Green and MI_Dino.

```{r, warning=FALSE, message=FALSE}
Green_Symbionts <- health_data %>% 
  select(-c(Event, Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, Nb_Tentacles, Weight_Total_g,
            Weight_Tube_g, Weight_Tentacle_g, Green_Cells, Dino_Cells, Feeding_Time_Min, Feeding_Time, Feeding_Start,
            Feeding_Stop, Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, Event_True)) %>% 
  filter(Date == "11/5/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021", "11/13/2021")) %>% 
  mutate(Green_Density_Log = log(Green_Density)) %>% 
  drop_na(Green_Density) %>% 
  drop_na(Dino_Density) %>% 
  drop_na(MI_Green) %>% 
  drop_na(MI_Dino) %>% 
  filter(Green_Density != 0) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period)) %>% 
  group_by(Treatment, Date) %>% 
  mutate(Mean_Green_Log = mean(Green_Density_Log), SE_Green_Log = std.error(Green_Density_Log))

Dino_Symbionts <- health_data %>% 
  select(-c(Event, Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, Nb_Tentacles, Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, Green_Cells, Dino_Cells, Feeding_Time_Min, Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, Event_True)) %>% 
  filter(Date == "11/5/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021", "11/13/2021")) %>% 
  drop_na(Green_Density) %>% 
  drop_na(Dino_Density) %>% 
  drop_na(MI_Green) %>% 
  drop_na(MI_Dino) %>% 
  filter(Dino_Density != 0) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period))
```

Checking Normality and Equal Variance:
```{r, warning=FALSE, message=FALSE}
#Green
shapiro.test(Green_Symbionts$Green_Density)      #p-value < 0.05, not normal distribution
bartlett.test(Green_Density ~ Treatment, Green_Symbionts)      #p-value < 0.05, does not meet assumption of equal variance

#Dino
shapiro.test(Dino_Symbionts$Dino_Density)      #p-value < 0.05, not normal distribution
bartlett.test(Dino_Density ~ Treatment, Dino_Symbionts)      #p-value < 0.05, meets assumption of equal variance
```

Checking Distributions:
We first test distributions learned in class to see if they fit those with the normal data. We repeat this for both Green and Dino density.

```{r, warning=FALSE, message=FALSE}
#Greens
exp_test(Green_Symbionts$Green_Density)         #p-value < 0.05
gamma_test(Green_Symbionts$Green_Density)       #p-value > 0.05, larger i can use, p = 0.123
lnorm_test(Green_Symbionts$Green_Density)       #p-value < 0.05
normal_test(Green_Symbionts$Green_Density)      #p-value < 0.05, not a normal distribution
weibull_test(Green_Symbionts$Green_Density)     #p-value > 0.05, larger i can use, p = 0.44

#Use Weibull since p value is larger than gamma
Green_Weibull <- histDist(Green_Symbionts$Green_Density, "WEI", density = F, main = "Weibull")

#Dinos
exp_test(Dino_Symbionts$Dino_Density)           #p-value > 0.05
gamma_test(Dino_Symbionts$Dino_Density)         #p-value > 0.05, larger i can use, p = 0.6709
lnorm_test(Dino_Symbionts$Dino_Density)         #p-value < 0.05
normal_test(Dino_Symbionts$Dino_Density)        #p-value < 0.05, not a normal distribution
weibull_test(Dino_Symbionts$Dino_Density)       #p-value > 0.05, larger i can use, p = 0.774

#Use Gamma since p value is larger than weibull
Dino_Gamma <- histDist(Dino_Symbionts$Dino_Density, "GA", density = F, main = "Gamma")
```

Running Models:
We chose to use our Weibull distribution for green density and Gamma distribution for dino density. Here we run our models.
```{r, warning=FALSE, message=FALSE}
#Green
Green_Symbionts$orderTreatment = ordered(Green_Symbionts$Treatment, levels = c("Control", "25C", "30C"))

Green_Weibull_model <- gamlss(formula = Green_Density ~ Date*Treatment + random(Species_ID) + random(Field_Site) + random(Acclimation_Period), family = WEI(), data = Green_Symbionts, control = gamlss.control(n.cyc = 10))
summary(Green_Weibull_model)

#Dino
Dino_Symbionts$orderTreatment = ordered(Dino_Symbionts$Treatment, levels = c("Control", "25C", "30C"))

Dino_Gamma_model <- gamlss(formula = Dino_Density ~ Date*Treatment + random(Species_ID) + random(Field_Site) + random(Acclimation_Period), family = GA(), data = Dino_Symbionts, control = gamlss.control(n.cyc = 3))
summary(Dino_Gamma_model)
```
The green density data was run with a weibull distribution. This model shows significance in 30C treatment.
Data from running with time points

Plots:
```{r, warning=FALSE, message=FALSE}
green_plot <- ggplot(Green_Symbionts, aes(x = Date, y = Green_Density)) +
  geom_boxplot() +
  xlab("Event") +
  ylab("Green algae density") +
  facet_grid(. ~ Treatment) +
  theme_test()
green_plot + scale_x_discrete(labels=c("11/5/2021" = "Pre-heat", "11/9/2021" = "Post-heat",
                              "11/13/2021" = "Recovery"))
```

```{r}
ggplot(filter(Green_Symbionts, Date ==  "11/9/2021"), aes(x = Treatment, y = log(Green_Density + 1))) +
  geom_boxplot() #+
  xlab("Treatment") +
  ylab("Green algae density") +
  theme_test()
```

```{r, warning=FALSE, message=FALSE}
dino_plot <- ggplot(Dino_Symbionts, aes(x = Date, y = Dino_Density, fill = Treatment)) +
  geom_boxplot() +
  xlab("Event") +
  ylab("Dinoflagelatte density") +
  theme_test()
dino_plot + scale_x_discrete(labels=c("11/5/2021" = "Pre-heat", "11/9/2021" = "Post-heat",
                              "11/13/2021" = "Recovery"))
```

```{r}
ggplot(filter(Dino_Symbionts, Date ==  "11/9/2021"), aes(x = Treatment, y = Dino_Density)) +
  geom_boxplot() +
  xlab("Event") +
  ylab("Dinoflagellate algae density") +
  theme_test()
```

```{r}
delta_green_density <- ggplot(delta_data, aes(x = Treatment, y = Delta_Green_Density)) +
  geom_boxplot() +
  ylab("Delta green algae density") +
  theme_test()
delta_green_density
```

```{r}
delta_dino_density <- ggplot(delta_data, aes(x = Treatment, y = Delta_Dino_Density)) +
  geom_boxplot() +
  ylab("Delta dinoflagellate density") +
  theme_test()
delta_dino_density
```

```{r}
green_over_time <- ggplot(data = Green_Symbionts, aes(x=Date, y = Mean_Green_Log, colour = Treatment, group = Treatment)) +
  theme_classic() +
  # geom_vline(xintercept = as.POSIXct("2021-11-06 09:00:00"),
  #            linetype = "dotted", 
  #            size = 1) +
  # geom_vline(xintercept = as.POSIXct("2021-11-08 16:00:00"), 
  #            linetype = "dotted", 
  #            size = 1)+
  geom_point(size=2.5) +
  geom_linerange(aes(ymin = Mean_Green_Log - SE_Green_Log, 
                    ymax = Mean_Green_Log + SE_Green_Log)) +
  geom_line() +
  labs(x="Date", 
       y = "Mean Green") +
  scale_fill_manual(values = cols_for_heat) +
  scale_colour_manual(values = cols_for_heat)
green_over_time
``````````````

### EXTRA DENSITY CALCULATIONS - NOT USING 
Log Transformations:
Next we run log transformations on our data and re-run the shapiro test to see if it has transformed our data to be more normal. We also mutate the data in order for the dataset to not contain 0s since we are running a log transformation. We repeat this for both Green and Dino density.
```{r, warning=FALSE, message=FALSE}
#Green
Green_log <- Green_Symbionts %>% mutate(log_data = log(abs(Green_Density + 0.01)))

shapiro.test(Green_log$log_data)      #p-value < 0.05, not normal distribution

#Dino
Dino_log <- Dino_Symbionts %>% mutate(log_data = log(abs(Dino_Density + 0.01)))

shapiro.test(Dino_log$log_data)      #p-value < 0.05, not normal distribution
```

Gaussian Transformation:
Both log transformations did not make the data normal, so I will try a Gaussian transformation. 
```{r, warning=FALSE, message=FALSE}
#Green
Green_gaussian <- Green_Symbionts %>% mutate(gaus_data = Gaussianize(Green_Symbionts$Green_Density, 's'))
shapiro.test(Green_gaussian$gaus_data)      #p-value < 0.05, not normal distribution, p = 3.19e-05

#Dino
Dino_gaussian <- Dino_Symbionts %>% mutate(gaus_data = Gaussianize(Dino_Symbionts$Dino_Density, 's'))
shapiro.test(Dino_gaussian$gaus_data)      #p-value > 0.05, normal distribution, p = 0.106

Dino_gaussian_plot <- ggplot(Dino_gaussian, aes(x = gaus_data)) + 
  geom_density() + 
  theme_classic() + 
  geom_vline(xintercept = 0, colour = "red")
```
The Gaussian transformation did not work on green density, when we ran a shapiro test for normality we got a p value smaller than 0.05. The transformation worked on the dino density. After visualizing the data, I think we will stick with the Weibell and Gamma distributions for green and dino density respectively.

### Mitotic Index Data
```{r}
MI_Data <- health_data %>% 
  select(-c(Event, Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, Nb_Tentacles, Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, Green_Cells, Dino_Cells, Feeding_Time_Min, Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, Event_True)) %>% 
  filter(Date == "11/5/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021", "11/13/2021")) %>% 
  drop_na(Green_Density) %>% 
  drop_na(Dino_Density) %>% 
  drop_na(MI_Green) %>% 
  drop_na(MI_Dino) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period))
```

Transformation of Data:
```{r}
#Green
MIGreen_log <- MI_Data %>% mutate(MI_Data = log(abs(MI_Green + 0.01)))
shapiro.test(MIGreen_log$MI_Data)      #p-value < 0.05, not normal distribution

#Dino
MIDino_log <- MI_Data %>% mutate(MI_Data = log(abs(MI_Dino + 0.01)))
shapiro.test(MIDino_log$MI_Data)      #p-value < 0.05, not normal distribution
```

Checking Distributions:
We tried a log and Gaussian transformation and both did not work, so we are running these models.

MI GREEN AND MI DINO NOT FOUND *** trouble shoot 
```{r, warning=FALSE, message=FALSE}
#Greens
exp_test(MI_Data$MI_Green)         #p-value = NA
gamma_test(MI_Data$MI_Green)       #p-value = NA
lnorm_test(MI_Data$MI_Green)       #p-value = NA
normal_test(MI_Data$MI_Green)      #p-value < 0.05, not normal
weibull_test(MI_Data$MI_Green)     #p-value = NA

MIGreen_fit <- fitDist(MI_Green, data = MI_Data, type = "realAll", try.gamlss = T)
#family JSUo 
MIGreen_hist <- histDist(MI_Data$MI_Green, "JSUo", density = F, main = "Johnson")

#Dinos
exp_test(MI_Data$MI_Dino)           #p-value = NA
gamma_test(MI_Data$MI_Dino)         #p-value = NA
lnorm_test(MI_Data$MI_Dino)         #p-value = NA
normal_test(MI_Data$MI_Dino)        #p-value < 0.05, not normal
weibull_test(MI_Data$MI_Dino)       #p-value = NA

Dino0 <- MI_Data %>%
  mutate(MI_Dino_scaled = MI_Dino + 0.01)

MIDino_fit <- fitDist(MI_Dino_scaled, data = Dino0, type = "realAll", try.gamlss = T)
#family SHASHo
MIDino_hist <- histDist(Dino0$MI_Dino_scaled, "SHASHo", density = T, main = "SHASHo")
```

Running Models:
```{r}
#Green
MI_Data$orderTreatment = ordered(MI_Data$Treatment, levels = c("Control", "25C", "30C"))

Green_JSUo_model <- gamlss(formula = MI_Green ~ Date*Treatment + random(Species_ID) + random(Field_Site) + random(Acclimation_Period), family = JSUo(), data = MI_Data, control = gamlss.control(n.cyc = 250))
summary(Green_JSUo_model)

#Dino
MI_Data$orderTreatment = ordered(MI_Data$Treatment, levels = c("Control", "25C", "30C"))

test <- Dino0 %>%
  mutate(Treatment = fct_relevel(Treatment, "Control", "25C", "30C"))

Dino_SHASHo_model <- gamlss(formula = MI_Dino_scaled ~ Date*Treatment + random(Species_ID) + random(Field_Site) + random(Acclimation_Period), family = SHASHo(), data = test, control = gamlss.control(n.cyc = 250))
summary(Dino_SHASHo_model)
```

### PAM data
```{r}
PAM_individuals <- health_data %>% 
  filter(Green_Density > 1000 | Dino_Density > 1000) %>% 
  distinct(Species_ID)

PAM_data <- health_data %>% 
  select(-c(Base_Width, Base_Length, Base_Diagonal, Base_Diameter_mm, Nb_Tentacles,
            Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, Green_Cells, Dino_Cells, 
            Feeding_Time_Min, Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, Removed, Div_Green, Div_Dino, 
            MI_Green, MI_Dino)) %>%
  drop_na(Time_Point) %>%
  drop_na(PAM_avg) %>%
  group_by(Treatment, Date) %>% 
  mutate(PAM_per_Treatment = mean(PAM_avg))

filtered_PAM_data = PAM_individuals %>%
  left_join(PAM_data) %>% 
  select(-c(Green_Density, Dino_Density))
```
  
```{r, warning=FALSE, message=FALSE}
shapiro.test(filtered_PAM_data$PAM_avg) # p-value < 0.05, distribution is not normal
bartlett.test(PAM_avg ~ Treatment, data = filtered_PAM_data) # p-value < 0.05, does not meet equal variance assumptions
```

Our data does not meet the assumption and therefore we will not be able to use tests such as ANOVA and linear models. 

Checking distribution:
If we get get a p-value < 0.5, then they is a significant differnce between the data and the distribution, and therefore this model should not be used in our analyse.

```{r, warning=FALSE, message=FALSE}
exp_test(filtered_PAM_data$PAM_avg)        #p-value < 0.05, cannot use
gamma_test(filtered_PAM_data$PAM_avg)      #p-value < 0.05, cannot use
lnorm_test(filtered_PAM_data$PAM_avg)      #p-value < 0.05, cannot use
normal_test(filtered_PAM_data$PAM_avg)     #p-value < 0.05, cannot use
weibull_test(filtered_PAM_data$PAM_avg)    #p-value < 0.05, cannot use
```

Since we cannot use any that we learned in class, we are using fitDist to check many distributions at once. fitDist showed that the SHASH distribution fits the best with our data, so we can use histDist to visualize it. 

**SHASH Distribution Graph for PAM Data**
```{r, warning=FALSE, message=FALSE}
#Look for anemone resiliancy Fv/Fm

PAM_visual <- fitDist(PAM_avg, data = filtered_PAM_data, type = "realAll", try.gamlss = T)
PAM_visual

#Visualizing fistDist

histDist(y, family = SHASH, density = FALSE, 
        nbins = 10, xlab = "x", ylab = "y", data = PAM_visual, 
        col.hist = "gray", border.hist = "blue", 
        fg.hist = rainbow(12)[9])
```

This data tells us to use the SHASH distribution for our PAM model. 

```{r, warning=FALSE, message=FALSE}
# Modelling fitDist
PAM_model <- gamlss(formula = PAM_avg ~ Time_Point*Treatment + random(Species_ID), family = SHASH(), data = filtered_PAM_data, control = gamlss.control(n.cyc = 22))

summary(PAM_model)
```

Findings:
* Time point and 25C is significant, 30C is not
* Plot avg fv/fm over all time points (this was significantly different over time)

**PAM graphs**
```{r}
PAM_avg_plot <- ggplot(data = filtered_PAM_data, aes(x = Time_Point, y = PAM_per_Treatment, color = Treatment)) +
  geom_line() +
  geom_point(size = 1) +
  xlab("Time Point") +
  ylab("PAM Measurements") +
  scale_color_manual(values = cols_for_heat)  +
  scale_fill_manual(values = cols_for_heat) +
  theme_test() +
  geom_segment(aes(x = 2.75, y = 0.2, xend = 2.75, yend = 0.75), size = 0.5 ,linetype = 2, colour = "black") +
  geom_segment(aes(x = 8.25, y = 0.2, xend = 8.25, yend =0.75), size= 0.35, linetype = 2, colour = "black")
PAM_avg_plot
```

### Size Data
```{r}
Size_Data <- health_data %>% 
  select(-c(Base_Width, Base_Length, Base_Diagonal, Nb_Tentacles, Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, Weight_Tentacle_mg, Green_Cells, Dino_Cells, Feeding_Time_Min, Feeding_Time, Feeding_Start, Feeding_Stop, Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, Green_Density, Dino_Density, MI_Green, MI_Dino, Div_Green, Div_Dino)) %>%
  filter(Date == "11/5/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021", "11/13/2021")) %>% 
  drop_na(Base_Diameter_mm) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period))
```

Running test of normality and equal variance on size data. 
```{r, warning=FALSE, message=FALSE}
shapiro.test(Size_Data$Base_Diameter_mm) # p-value = 0.0002, distribution is not normal
bartlett.test(Base_Diameter_mm ~ Treatment, data = Size_Data) # p-value = 0.15, yay equal variance
```

Checking Distribution:
```{r}
exp_test(Size_Data$Base_Diameter_mm)            #p-value < 0.05
gamma_test(Size_Data$Base_Diameter_mm)          #p-value > 0.05, p = 0.1874
lnorm_test(Size_Data$Base_Diameter_mm)          #p-value > 0.05, p = 0.4117
normal_test(Size_Data$Base_Diameter_mm)         #p-value < 0.05, not normal
weibull_test(Size_Data$Base_Diameter_mm)        #p-value < 0.05

# Run lnorm since it has the higest p value
Size_lnorm <- histDist(Size_Data$Base_Diameter_mm, "LOGNO", density = T, main = "lNorm")

#which has the best distribution? - compare AIC values
Size_lnorm <- histDist(Size_Data$Base_Diameter_mm, "LOGNO", density = T, main = "lNorm")
#AIC = 880.625
Feeding_Gamma <- histDist(Size_Data$Base_Diameter_mm, "GA", density = F, main = "Gamma")
#AIC = 883.161
```

Running Models:
We are going to run a lNorm model on our size data because the p value is larger and AIC value is smaller. 

```{r}
Size_Data$orderTreatment = ordered(Size_Data$Treatment, levels = c("Control", "25C", "30C"))

Size_lNorm_model <- gamlss(formula = Base_Diameter_mm ~ Date*Treatment + random(Species_ID) + random(Field_Site) + random(Acclimation_Period), family = LOGNO(), data = Size_Data, control = gamlss.control(n.cyc = 4))
summary(Size_lNorm_model)
```
We have significance in our 30C treatment. 

**Size Graph**
```{r, warning=FALSE, message=FALSE}
 ggplot(Size_Data, aes(x = Date, y = Base_Diameter_mm)) +
  geom_boxplot() +
  facet_grid(. ~ Treatment) +
  theme_test()
```

### Feeding Data
```{r, warning=FALSE, message=FALSE}
Feeding_Data <- health_data %>% 
  select(-c(Base_Width, Base_Length, Base_Diagonal, Nb_Tentacles, Weight_Total_g, Weight_Tube_g, Weight_Tentacle_g, Weight_Tentacle_mg, Green_Cells, Dino_Cells, Base_Diameter_mm, Photo_ID, Removed, Fv_Fm_1, Fv_Fm_2, Fv_Fm_3, PAM_avg, Green_Density, Dino_Density, MI_Green, MI_Dino, Div_Green, Div_Dino)) %>%
  filter(Date == "11/5/2021" | Date == "11/9/2021" | Date == "11/13/2021") %>% 
  mutate(Date = fct_relevel(Date, "11/5/2021", "11/9/2021", "11/13/2021")) %>% 
  drop_na(Feeding_Time_Min) %>% 
  mutate(Acclimation_Period = as.factor(Acclimation_Period))
```

Running test of normality and equal variance on feeding data. 
```{r, warning=FALSE, message=FALSE}
shapiro.test(Feeding_Data$Feeding_Time_Min)                      # p-value < 0.05, distribution is not normal
bartlett.test(Feeding_Time_Min ~ Treatment, data = Feeding_Data) # p-value < 0.05, no equal variance 
```

The data is not equal or normal, so we're are going to check distributions to see what fits best. 
```{r, warning=FALSE, message=FALSE}
exp_test(Feeding_Data$Feeding_Time_Min)            #p-value < 0.05
gamma_test(Feeding_Data$Feeding_Time_Min)          #p-value > 0.05, p = 0.3717, usable
lnorm_test(Feeding_Data$Feeding_Time_Min)          #p-value > 0.05, p = 0.6937, usable
normal_test(Feeding_Data$Feeding_Time_Min)         #p-value < 0.05, not normal
weibull_test(Feeding_Data$Feeding_Time_Min)        #p-value > 0.05, p = 0.088, usable

#which has the best distribution? - compare AIC values
Feeding_lnorm <- histDist(Feeding_Data$Feeding_Time_Min, "LOGNO", density = T, main = "lNorm") 
#AIC = 112.738
Feeding_Gamma <- histDist(Feeding_Data$Feeding_Time_Min, "GA", density = F, main = "Gamma")
#AIC = 116.789
Green_Weibull <- histDist(Feeding_Data$Feeding_Time_Min, "WEI", density = F, main = "Weibull")
#AIC = 115.143
```

Running model:
We are going to use the lnorm distribution because the p value is larger and AIC value is smaller.
```{r, warning=FALSE, message=FALSE}
Feeding_Data$orderTreatment = ordered(Feeding_Data$Treatment, levels = c("Control", "25C", "30C"))

Feeding_lNorm_model <- gamlss(formula = Feeding_Time_Min ~ Date*Treatment + random(Species_ID) + random(Field_Site) + random(Acclimation_Period), family = LOGNO(), data = Feeding_Data, control = gamlss.control(n.cyc = 3))
summary(Size_lNorm_model)
```

Plot:
```{r, warning=FALSE, message=FALSE}
feeding_plot <- ggplot(Feeding_Data, aes(x = Date, y = Feeding_Time_Min, fill = Treatment)) +
  geom_boxplot(alpha=0.85) +
  xlab("Event") +
  ylab("Feeding Time (minutes)") +
  scale_color_manual(values = cols_for_heat) +
  scale_fill_manual(values = cols_for_heat) +
  theme_test()
feeding_plot <- feeding_plot + scale_x_discrete(labels=c("11/5/2021" = "Pre-heat", "11/9/2021" = "Post-heat",
                              "11/13/2021" = "Recovery"))
feeding_plot
```

## Heat Data
Includes temperature during heatwave and behavioral responses (open vs closed)

```{r, warning=FALSE, message=FALSE}
heat_data <- heat_data %>% 
  mutate(Open_Closed = as.factor(Open_Closed), Bucket = as.factor(Bucket), 
         Treatment = as.factor(Treatment), Field_Site = as.factor(Field_Site)) %>% 
  mutate(Open_Closed = fct_relevel(Open_Closed, "Open", "Partial", "Closed")) %>% 
  mutate(Treatment = fct_relevel(Treatment, "Control", "25C", "30C")) %>% 
  group_by(Treatment, Time_Block) %>% 
  mutate(Temp_avg = mean(Bucket_Temp))
```

**Temperature over time Graph**
```{r, warning=FALSE, message=FALSE}
heat_plot <- ggplot(data = heat_data, aes(x = Time_Block, y = Temp_avg, color = Treatment)) +
  geom_point(size = 1) +
  geom_line(alpha = 1.5) +
  xlab("Time (hours)") +
  ylab("Temperature (°C)") +
  scale_color_manual(values = cols_for_heat) +
  scale_fill_manual(values = cols_for_heat) +
  theme_test()
heat_plot
```

### Ordinal Regression
```{r}
ord_model = clmm(Open_Closed ~ Treatment + (1 | Bucket) + (1 | Species_ID), data = heat_data)
summary(ord_model)
```

**Open/Closed Graph**
```{r, warning=FALSE, message=FALSE}
cols_for_behaviour = c("Open" = "bisque1", "Partial" = "brown2", "Closed" = "darkred")
behaviour_data <- heat_data %>% 
  group_by(Day, Treatment, Time_Block) %>% 
  count(Open_Closed)

behaviour_plot <- ggplot(data = behaviour_data, aes(x = Time_Block, y = n, fill = Open_Closed)) + 
  geom_bar(position="fill", stat="identity") +
  facet_grid(. ~ Treatment) +
  xlab("Time (hours)") +
  ylab("Frequency") +
  scale_fill_brewer(palette = "Reds") +
  theme_cowplot()
behaviour_plot <- behaviour_plot + labs(fill = "Behaviour Response")

ggsave(here("./images/behaviour_plot.png"), behaviour_plot)
```

